|

### 2022-05-28 memorandum/memo.Rmd
fix spacing memo

We now cite Gerring and Veenendaal's book four times. We mention it twice on
page 2: ``\textit{Legislature size has a significant effect on collective action
strategies, the bargaining power between state branches, government spending,
and representation \citep{crain1979cost, freire2021legislature,
gerring2020population, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
However, how legislature size impacts social welfare remains less understood.
Larger legislatures may reduce political particularism and increase overall
government spending, which leads to more public goods
\citep{gerring2020population, GilliganMatsusaka2001, Weingastetal1981}}.'' We
mention it again on page 4: ``\textit{Following the seminal contribution by
\citet{Weingastetal1981}, the "law of $1/n$" posits that larger legislatures
increase the legislative pressure for providing targeted public goods to local
supporters at the expense of the entire polity \citep{freire2021legislature}.
This question has become more relevant since legislature size has increased
consistently over time \citep{gerring2020population}}.'' Finally, we also cite
the book on page 5: ``\textit{On the one hand, larger legislatures improve
representation and facilitate the electoral success of ethnic and political
minorities\citep{allenrepresentation, gerring2020population}}.''

>>>>

We now cite Gerring and Veenendaal's book four times. We mention it twice on
page 2: ``\textit{Legislature size has a significant effect on collective action
strategies, the bargaining power between state branches, government spending,
and representation \citep{crain1979cost, freire2021legislature,
gerring2020population, PrimoSnyder2008, rogers2002free, Weingastetal1981}.
However, how legislature size impacts social welfare remains less understood.
Larger legislatures may reduce political particularism and increase overall
government spending, which leads to more public goods
\citep{gerring2020population, GilliganMatsusaka2001, Weingastetal1981}}.'' We
mention it again on page 4: ``\textit{Following the seminal contribution by
\citet{Weingastetal1981}, the "law of $1/n$" posits that larger legislatures
increase the legislative pressure for providing targeted public goods to local
supporters at the expense of the entire polity \citep{freire2021legislature}.
This question has become more relevant since legislature size has increased
consistently over time \citep{gerring2020population}}.'' Finally, we also cite
the book on page 5: ``\textit{On the one hand, larger legislatures improve
representation and facilitate the electoral success of ethnic and political
minorities \citep{allenrepresentation, gerring2020population}}.''
